Structural and Dybamical Divergence Analysis -  Comparisons

### 2017-06-25 analysis-dynamical-MSF-structure.Rmd
23/6/17

siteComparison.all.datasets.dri2 = ddply(siteComparison.all.datasets.dri2, c("dataset", "protein"), mutate,
          "RSD" = sqrt(dri2), 
        "z.RSD" = vscale(RSD))
```

@@

# dat with means and standard errors
d = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                n.data = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(n.data)
                data.frame(mean.z.RSD, n.data, se.z.RSD)
})

@@

mean.r.dri2.exp = d.exp$mean.z.RSD
mean.r.dri2.mut = d.mut$mean.z.RSD
mean.r.dri2.medium = d.medium$mean.z.RSD
```

>>>>

siteComparison.all.datasets.dri2 = ddply(siteComparison.all.datasets.dri2, c("dataset", "protein"), mutate,
          "RSD" = sqrt(dri2), 
           "SD" = dri2, 
        "z.RSD" = vscale(RSD),
         "z.SD" = vscale(SD))
```

@@

# dat with means and standard errors
d = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                mean.RSD = mean(x$RSD, na.rm = T)
                mean.z.SD = mean(x$z.SD, na.rm = T)
                mean.SD = mean(x$SD, na.rm = T)
                n.data = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(n.data)
                data.frame(mean.z.RSD,mean.RSD, mean.z.SD, mean.SD, n.data, se.z.RSD)
})

@@

mean.r.dri2.exp = d.exp$mean.z.RSD
mean.r.dri2.mut = d.mut$mean.z.RSD
mean.r.dri2.medium = d.medium$mean.z.RSD

# MSF.p.ref vs z.RSD and z.SD
MSF.p.ref = as.vector(MSF.p.ref)

## correlations
r.exp = cor(d.exp$mean.RSD, MSF.p.ref)
r.medium = cor(d.mut$mean.RSD, MSF.p.ref)
r.mut = cor(d.medium$mean.RSD, MSF.p.ref)

cor.df = data.frame("MSF vs RSD" = c("exp", "selection", "no-selection"),
                    "R" = c(r.exp, r.medium, r.mut))
knitr::kable(cor.df, digits = 2)

## plots

par(pty = "s")

plot(y = d.exp$mean.RSD, x = MSF.p.ref, ylab = "RSD experimental")
lm = lm(d.exp$mean.RSD ~ MSF.p.ref)
abline(lm)
legend("topleft", paste ("r = ", round(r.exp, digits = 2)), bty = "n")

plot(y = d.mut$mean.RSD, x = MSF.p.ref, ylab = "RSD no-selection")
lm = lm(d.mut$mean.RSD ~ MSF.p.ref)
abline(lm)
legend("topleft", paste ("r = ", round(r.mut, digits = 2)), bty = "n")

plot(y = d.medium$mean.RSD, x = MSF.p.ref, ylab = "RSD selection")
lm = lm(d.medium$mean.RSD ~ MSF.p.ref)
abline(lm)
legend("topleft", paste ("r = ", round(r.medium, digits = 2)), bty = "n")

## correlations
r.exp = cor(d.exp$mean.SD, MSF.p.ref)
r.medium = cor(d.mut$mean.SD, MSF.p.ref)
r.mut = cor(d.medium$mean.SD, MSF.p.ref)

cor.df = data.frame("MSF vs SD" = c("exp", "selection", "no-selection"),
                    "R" = c(r.exp, r.medium, r.mut))
knitr::kable(cor.df, digits = 2)

## plots
par(pty = "s")

plot(y = d.exp$mean.SD, x = MSF.p.ref, ylab = "SD experimental")
lm = lm(d.exp$mean.SD ~ MSF.p.ref)
abline(lm)
legend("topleft", paste ("r = ", round(r.exp, digits = 2)), bty = "n")

plot(y = d.mut$mean.SD, x = MSF.p.ref, ylab = "SD no-selection")
lm = lm(d.mut$mean.SD ~ MSF.p.ref)
abline(lm)
legend("topleft", paste ("r = ", round(r.mut, digits = 2)), bty = "n")

plot(y = d.medium$mean.SD, x = MSF.p.ref, ylab = "SD selection")
lm = lm(d.medium$mean.SD ~ MSF.p.ref)
abline(lm)
legend("topleft", paste ("r = ", round(r.medium, digits = 2)), bty = "n")

### 2017-06-25 analysis-structure-normal-modes.Rmd
23/6/17

>>>>

p = ggplot(dat,aes(x=mode,y=Pn.median,col=dataset,fill=dataset)) +
    geom_pointrange(aes(ymin=Pn.median.min,ymax = Pn.median.max),size=.2,alpha=.4) +
    geom_line(aes(y=rq.5))  +
    labs(x="mode energy",y="structural divergence (median Pn) ") +
    scale_colour_manual(name = NULL,values = myColors) + 
    scale_fill_manual(name=NULL,values=myColors)+
    coord_cartesian(xlim=c(0,3))

p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
p.facet %+% subset(dat,dataset == "exp")
p.facet %+% subset(dat,dataset == "no-selection")
p.facet %+% subset(dat,dataset == "selection")
p.facet
p + theme(legend.position = "bottom")
```

### 2017-06-25 analysis-structure.Rmd
23/6/17

plot(x = d.exp$mean.z.RSD, y = log(CN), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(CN), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
```

>>>>

plot(x = d.exp$mean.z.RSD, y = (1/CN), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = (1/CN), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = (1/CN), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, (1/CN))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, (1/CN))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, (1/CN))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs 1/CN", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs 1/CN"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (1/CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, (1/CN), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, (1/CN), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, (1/CN), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs 1/CN", "<z.RSD> no-selection vs 1/CN", "<z.RSD> selection vs 1/CN"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (1/CN)")
```

### 2017-06-25 comparison_families.Rmd
23/6/17

@@

@@

@@

>>>>

## comparison mut - sel
plot(x = cc.z.RSD_CA[,3], y = cc.z.RSD_CA[,6], xlab = "cc <z.RSD> exp - <z.RSD> no-selection", ylab = "cc <z.RSD> exp - <z.RSD> selection")
abline(0,1)
legend("topleft", paste ("r = ", round(cor(cc.z.RSD_CA[,3], cc.z.RSD_CA[,6]), digits = 2)), bty = "n")

@@

plot(x = cc.Pn_CA[,3], y = cc.Pn_CA[,6], xlab = "cc <Pn> exp -  <Pn> no-selection", ylab = "cc <Pn> exp -  <Pn> selection")
abline(0,1)
legend("topleft", paste ("r = ", round(cor(cc.Pn_CA[,3], cc.Pn_CA[,6]), digits = 2)), bty = "n")

@@

## comparison mut - sel
plot(x = cc.MSF_CA[,3], y = cc.MSF_CA[,6], xlab = "cc <MSF> exp - <MSF> no-selection", ylab = "cc <MSF> exp -  <MSF> selection")
abline(0,1)
legend("topleft", paste ("r = ", round(cor(cc.MSF_CA[,3], cc.MSF_CA[,6]), digits = 2)), bty = "n")

@@

## comparison mut - sel
plot(x = cc.nH_CA[,3], y = cc.nH_CA[,6], xlab = "cc <nH> exp -  <MSF> no-selection", ylab = "cc <nH> exp -  <MSF> selection")
abline(0,1)
legend("topleft", paste ("r = ", round(cor(cc.nH_CA[,3], cc.nH_CA[,6]), digits = 2)), bty = "n")
